\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2011-03-24 inst/doc/Foreword.tex
Added the MSnbase package to the repository.
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@54004 bc3139a8-67e5-0310-9ffc-ced21a209358

\Rpackage{MSnbase} is in an early development %%(package version \Sexpr{packageVersion("MSnbase")}, 
(see section \ref{sec:sessionInfo} for details about packages and version used in this vignette). 
Although main data structures have been thought out and are meant to be compatible with other existing 
mature infrastructure in the Bioconductor project, changes may occur in the future. 
Current functionality will evolve and new ones will be added. 
Although at an early stage, this package is released in the hope that it may foster  
new developments in proteomics data analysis within \R by providing a common infrastructure. 
Several package developers related to mass spectrometry and proteomics data met during the 
Bioconductor Developer Meeting Europe\footnote{\url{http://bioconductor.org/help/course-materials/2010/HeidelbergNovember2010/}} 
held in Heidelberg in November 2010, and agreed to combine efforts. 
This library is one attempt to do so.

>>>>

\Rpackage{MSnbase} is in an early development %%(package version \Sexpr{packageVersion("MSnbase")}, 
(see section \ref{sec:sessionInfo} for details about packages and version used in this vignette). 
Although main data structures have been thought out and are meant to be compatible with other existing 
mature infrastructure in the Bioconductor project, changes may occur in the future. 
Current functionality will evolve and new one will be added. 
Although at an early stage, this package is released in the hope that it may foster  
new developments in proteomics data analysis within \R by providing a common infrastructure. 
Several package developers working with mass spectrometry and proteomics data met at the 
Bioconductor Developer Meeting Europe\footnote{\url{http://bioconductor.org/help/course-materials/2010/HeidelbergNovember2010/}} 
held in Heidelberg in November 2010, and agreed to combine efforts. 
This library is one attempt to do so.

### 2011-03-24 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
Added the MSnbase package to the repository.
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@54004 bc3139a8-67e5-0310-9ffc-ced21a209358

%\VignetteIndexEntry{Base Functions and Classes for MS-based Proteomics }
%\VignetteKeywords{Mass Spectrometry, MS, MSMS, Proteomics, Infrastructure, Bioinformatics, quantitative }
%\VignettePackage{MSnbase-demo}
\documentclass{article}
\usepackage{tikz}
\usepackage[nogin]{Sweave}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}

@@

\begin{figure}[!ht]
<<spectrum-plot,fig=T,echo=T,tikz=T,external=T,width=5,height=5>>=
plot(sp,reporters=iTRAQ4,full=TRUE)
@ 
\caption{Raw MS2 spectrum with details about reporter ions.}
\label{fig:spectrum-plot}
\end{figure}

@@

\begin{figure}[!ht]
<<msnexp-plot,fig=T,echo=T,tikz=T,external=T,width=5,height=6>>=
plot(exp2,reporters=iTRAQ4,full=FALSE)
@ 
\caption{Experiment-wide raw MS2 spectra.}
\label{fig:msnexp-plot}
\end{figure}

@@

\begin{figure}[!ht]
<<spectrum-plot2,fig=T,echo=T,tikz=T,external=T,width=5,height=5>>=
plot(experiment[["X43"]],reporters=iTRAQ4,full=TRUE)
@ 
\caption{Same spectrum as on figure \ref{fig:spectrum-plot}, 
  after setting peaks <= 3 to 0.}
\label{fig:spectrum-plot2}
\end{figure}

>>>>

%\VignetteIndexEntry{Base Functions and Classes for MS-based Proteomics}
%\VignetteKeywords{Mass Spectrometry, MS, MSMS, Proteomics, Infrastructure, Bioinformatics, quantitative }
%\VignettePackage{MSnbase-demo}
\documentclass{article}
\usepackage{tikz}
\usepackage[nogin]{Sweave}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}

@@

\begin{figure}[!ht]
<<spectrum-plot,fig=T,echo=T,tikz=T,external=F,width=5,height=5>>=
plot(sp,reporters=iTRAQ4,full=TRUE)
@ 
\caption{Raw MS2 spectrum with details about reporter ions.}
\label{fig:spectrum-plot}
\end{figure}

@@

\begin{figure}[!ht]
<<msnexp-plot,fig=T,echo=T,tikz=T,external=F,width=5,height=6>>=
plot(exp2,reporters=iTRAQ4,full=FALSE)
@ 
\caption{Experiment-wide raw MS2 spectra.}
\label{fig:msnexp-plot}
\end{figure}

@@

\begin{figure}[!ht]
<<spectrum-plot2,fig=T,echo=T,tikz=T,external=F,width=5,height=5>>=
plot(experiment[["X43"]],reporters=iTRAQ4,full=TRUE)
@ 
\caption{Same spectrum as on figure \ref{fig:spectrum-plot}, 
  after setting peaks <= 3 to 0.}
\label{fig:spectrum-plot2}
\end{figure}
